|

### 2019-12-20 article/article.Rmd
small changes

**We discuss some possible reasons why community monitoring did not work in our
case**. ~~A~~ **One** plausible explanation is that individuals were unable to
differentiate the effect of political corruption from those of spending cuts.
Due to the severe economic crisis in 2014--2016, the Brazilian federal
government introduced discretionary spending limits that affected public
investment [@mello2016fix; @rossi2016impactos]. Politicians may argue that
delays in school constructions are not derived from their misuse of government
funds, but from the austerity measures. If this is the case, citizens will not
blame local politicians for the underprovision of public goods. Consequently,
representatives can dismiss individual requests as the issue is unlikely to
escalate.

>>>>

**We discuss some possible reasons why community monitoring did not work in our
case**. ~~A~~ **One** plausible explanation is that individuals were unable to
differentiate the effect of political corruption from those of spending cuts.
Due to the severe economic crisis in 2014--2016, the Brazilian federal
government introduced discretionary spending limits that affected public
investment [@rossi2016impactos]. Politicians may argue that
delays in school constructions are not derived from their misuse of government
funds, but from the austerity measures. If this is the case, citizens will not
blame local politicians for the underprovision of public goods. Consequently,
representatives can dismiss individual requests as the issue is unlikely to
escalate.
